---
title       : Bump Chart
subtitle    : Customizing Visualizations
---

<iframe src='fig/bchart2.html' width=100% height=600 seamless></iframe>

--- .segue .dark .nobackground

```{r setup, echo = F, cache = F}
library(knitr)
opts_chunk$set(tidy = F, fig.path = 'fig/')
read_chunk("global.R")
require(xtable)
options(xtable.type = 'html', xtable.include.rownames = F)
```

## Get Data

---

```{r echo = F, results = 'asis', comment = NA}
dat <- read.csv('data/E0-1112.csv')
xtable(head(dat[, c("Date", "HomeTeam", "AwayTeam", "FTR")], 15))
```

--- .segue .dark .nobackground

## Reshape Data

--- &tabs

***

## Code

```{r results = 'asis', ref.label = "getData"}

```

*** .active

## Data

```{r results = 'asis', echo = F, message = F, warning = F}
data_ <- getData('data/E0-1112.csv')
xtable(head(data_, 13))
```


--- .segue .dark .nobackground

## Get League Table

--- &tabs

*** 

## Code

```{r results = 'asis', ref.label = "getLeagueTable"}

```

*** .active

## Data

```{r results = 'asis', echo = F, message = F}
data_2 <- getLeagueTable("2012-05-13", data_)
xtable(head(data_2, 13))
```

--- .segue .dark .nobackground

## Get Bump Chart Data

--- &tabs

***

## Code

```{r results = 'asis', ref.label = "getBumpChartData"}

```

*** .active

## Data

```{r results = 'asis', echo = F, message = F}
data_3 <- getBumpChartData("data/E0-1112.csv")
xtable(head(data_3, 15))
```

--- .segue .dark .nobackground

## Visualize Data

--- &tabs .larger


*** .active 

## Code

```{r results = 'asis', ref.label = "plotBumpChart"}

```

***

## Plot

```{r bchart1, echo = F, results = 'asis', comment = NA}
b1 <- plotBumpChart(data_3)
b1
```

--- .segue .dark .nobackground

## Customize Popup

--- &tabs .larger

*** .active

## Code

```{r results = 'asis', comment = NA}
b1$yAxis(tickFormat = "#! function(n){
  return(n == 0 ? '': String(21 - n))
} !#")
b1$hoverDetail(formatter = "#! function(series, x, y){
  var info = series.info[String(x)];
  var d = new Date(x * 1000).toUTCString();
  return '<b>' + series.name + '</b><br><br>' + 
  '<b>Position:</b> ' + String(21 - y)  +
  '<br><b>Points:</b> ' + info.P +
  '<br><b>Wins:</b> ' + info.W +
  '<br><b>Draws:</b>' + info.D +
  '<br><b>Losses:</b>' + info.L +
  '<br><br>' + d
} !#")
```

***

## Plot

```{r bchart2, echo = F, results = 'asis', comment = NA}
b1
```

<style>
  li.tab::before{content: ""}
  slide.larger pre {
    font-size: 28px;
    line-height: 32px;  
  }
</style>
